A deeper look into bug fixes: Patterns, replacements, deletions, and additions

### 2016-02-17 MSRChallenge2016.tex
Moved some text from sec.5 to sec.1

Automatic bug repair is the branch of computer science that deals with automated
ways to repair errors in software. There have been several approaches taken
towards improving the different methodologies to repair bugs in software
automatically~\cite{kim2013,weimer2009,legoues2012,pan2009}. A well known approach is PAR~\cite{kim2013}, which creates 10 different repair templates and applies them to the buggy code in an effort to repair
it. In this paper we have taken 8 out of the 10 PAR templates and tested how
common they are in the repairs made by programmers in the latest official data
dump of Github as of September 2015 provided by~\cite{dyer2013}.

Some other well known approaches~\cite{weimer2009,legoues2012} have been based on the idea of applying a number of mutation operators to the buggy code in order to find a patch. In this opportunity, we study the degree to which these mutation operators apply in practice, taking as a subject of study several million human-made bug fixes from Github. This way it will make it more likely for automatic error repair approaches to succeed in
finding a patch for a particular error, and also, to provide automatic error
repair software with guidelines to make the patches more human-like and
therefore more readable and maintainable by human developers, as studied empirically by~\cite{kim2013}.

We take as reference the study performed by Dongsun Kim et al.~\cite{kim2013} in which they look for the most common ways in which programmers patch bugs in software. The
researchers developed a variation of the tool Genprog~\cite{weimer2009,legoues2012}
with several different templates resembling patterns programmers use to patch
bugs, and then performed an empirical study to evaluate which patches do human programmers prefer.

Since automatic program repair has been well studied in the programming language C. We are now focusing on the programming language Java, and analyzing the behavior of programmers in this particular language.

>>>>

Automatic bug repair is the branch of computer science that deals with
automated ways to repair errors in software. There have been several approaches
taken towards improving the different methodologies to repair bugs in software
automatically~\cite{kim2013,weimer2009,legoues2012,pan2009}. Roughly speaking,
there are two main categories of approaches.

On the one hand, some approaches rely on mutation operators to modify the source
code~\cite{legoues2012,weimer2009}. However, we have limited knowledge about
what kinds of statements are usually modified. In this opportunity, we study the
degree to which these mutation operators apply in practice, taking as a subject
of study several million human-made bug fixes from Github. This way it will make
it more likely for automatic error repair approaches to succeed in finding a
patch for a particular error, and also, to provide automatic error repair
software with guidelines to make the patches more human-like and therefore more
readable and maintainable by human developers, as studied empirically
by~\cite{kim2013}.

On the other hand, some approaches~\cite{kim2013} search for specific patterns
and modify source code according to predefined templates. A well known approach
is PAR~\cite{kim2013}, which creates 10 different repair templates and applies
them to the buggy code in an effort to repair it. In this paper we have taken 8
out of the 10 PAR templates and tested how common they are in the repairs made
by programmers in the latest official data dump of Github as of September 2015
provided by~\cite{dyer2013}.  Our results provide evidence of how common those
patterns are in practice. We take as reference the study performed by Dongsun
Kim et al.~\cite{kim2013} in which they look for the most common ways in which
programmers patch bugs in software. The researchers developed a variation of the
tool Genprog~\cite{weimer2009,legoues2012} with several different templates
resembling patterns programmers use to patch bugs, and then performed an
empirical study to evaluate which patches do human programmers prefer.

Although automatic program repair has been well studied in the programming language
C, not much study has been done on Java. Since the programming practice between
C and Java is not trivial, we will also show some characteristics of how human
developers fix bugs in Java.
